Measuring variation in gaze following across communities, ages, and individuals — a showcase of the TANGO-CC

### 2024-09-23 paper/manuscript.Rmd
revisions 1

---
title: "Measuring variation in gaze following across communities, ages, and individuals — a showcase of the TANGO--CC"
shorttitle: "measuring gaze following across communities"

@@

@@

    affiliation   : "10"

@@

@@

affiliation:
  - id            : "1"
    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany"
  - id            : "3"
    institution   : "School of Psychology, University of Auckland, New Zealand"
  - id            : "4"
    institution   : "Université Marien Ngouabi, Republic of the Congo"
  - id            : "5"
    institution   : "Department of Psychology, Stanford University, USA"
  - id            : "6"
    institution   : "School of Psychology, University of Plymouth, UK"
  - id            : "7"
    institution   : "Department of Psychology, Koç University, Türkiye"
  - id            : "8"
    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK"
  - id            : "9"
    institution   : "Department of Psychology and Social Work, University of Namibia, Namibia"
  - id            : "10"
    institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
  - id            : "11"
    institution   : "Department of Psychology, University of York, UK"
  - id            : "12"
    institution   : "Budongo Conservation Field Station, Uganda"
  - id            : "13"
    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
  - id            : "+"
    institution   : "joint last author"

abstract: | 
            Cross-cultural studies are crucial for investigating the cultural variability and universality of cognitive developmental processes. However, cross-cultural assessment tools in cognition across languages and communities are limited. This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO--CC). The task was developed and psychometrically assessed in one cultural setting and, with input of local collaborators, adapted for cross-cultural data collection. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community. The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities. Within-community variation outweighed between-community variation. We provide an open-source website for researchers to customize and use the task (https://ccp-odc.eva.mpg.de/tango-cc). The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.

@@

The approaches that researchers can take to collect cross-cultural data lie on a continuum: the decision for a specific method partly depends on whether researchers aim to increase the *depth* (culture specificity) or *breadth* (standardization across multiple communities) of their work [@amir2020crosscultural].
At one extreme, researchers translate the psychological construct into a separate design or task for each community (termed "assembly"; @he2012bias, @waschl2022crosscultural).
While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible to study a multitude of communities as it becomes too demanding and time-consuming.
Furthermore, the results are limited to each community and absolute task scores might not be comparable across communities.
A study following this approach is @wefers2023universality who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions. 
While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, @wefers2023universality reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (*i.e.,* emphasis on body stimulation) parenting styles. 
By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.

At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed "adoption" and "adaptation", respectively; [@he2012bias, @waschl2022crosscultural]).
This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; [@gagarina2012main]), which assesses narrative abilities in mono- and multilingual children. 
Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust, and suitable for cross-linguistic comparisons [@gagarina2012main], and new and revised language versions are continuously added to the MAIN database [@gagarina2020new].

The present paper aims to describe the development and psychometric properties of a social cognition task that can be adapted to diverse communities.
On the continuum described above, our task lies more toward standardized approaches but allows for some customization of the stimuli to each local community.
The task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
Gaze following develops early in infancy [@delbianco2019developmental; @tang2024slow] and contributes to social learning, communication, and collaboration [@shepherd2010following; @tomasello2007reliance; @bohn2018common; @hernik2019infant].
While the question of how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research [@astor2022gaze], studies focusing on cultural variations of gaze following are rare.
@callaghan2011early investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38), and India (n = 65). 
In their setup, an agent looked at a toy behind (experimental condition) or a sticker in front of (control condition) a barrier, and children's crawling toward the barrier to follow the agent's gaze was assessed.
While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier than in front of it.
@hernik2019infant studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
Even though face-to-face interactions are less common in parent-child interactions in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
While these two studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and – more importantly – does not allow for studying individual-differences. 
A more comprehensive cross-cultural study on gaze following was recently conducted by @bohn2024universal. The researchers tested the universality of gaze following by studying 17 different communities on five continents and found evidence for a similar processing mechanism across communities.

The task presented in this manuscript was developed for the study by @bohn2024universal and is based on a previously established gaze-following task called 'TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2023tango.
The TANGO measures how precisely participants locate an agent's attentional focus.
It reliably measured individual differences in a German child sample and an English-speaking remote adult sample [@prein2023tango].
However, we cannot claim the task's generalizability and reliability based on a mono-cultural sample. 
This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities [@bohn2024universal].
We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/tango-cc/>).

@@

The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity [@prein2023tango].
During this process, the cross-cultural adaptation of the task was prepared by a team of cross-cultural psychologists and cognitive scientists. 
In this paper, we assess the TANGO--CC's measurement quality (*i.e.,* variability and reliability) across 17 diverse communities by analyzing the data set from @bohn2024universal.
In the following, we describe the different steps in detail.

The TANGO--CC is a screen-based task that measures the imprecision with which participants locate a balloon by following an agent’s gaze (see Figure \@ref(fig:fig1)). 
Participants click or touch the location on the screen where they believe the balloon to be.
Precision is measured as the distance between the participant’s click on the screen and the balloon’s real position.

During the task development, we decided to implement the task's main functionality independently of the task's appearance. 
We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures. 
As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (*i.e.*, no coordination values for animation are hard-coded into the task's source code). 
After having programmed this "backbone" functionality of the task (*i.e.*, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).

This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid [@prein2023tango].
While children became more precise in locating the agent's attentional focus with age, individuals differed across all age groups and showed no floor- or ceiling effects.
In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
In a computational cognitive model, @prein2024variation described gaze following as a form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
These connections to related constructs indicate the task's convergent validity in the German child sample.

To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with input from local researchers and research assistants. 
The stimulus pool was adjusted and expanded until the researchers and research assistants from each target community judged the selected stimuli to be representative of the local population and typical accommodation (see Figure \@ref(fig:fig2)).
Audio instructions were translated from English or German into the corresponding local language(s).
By back-translating these instructions, we ensured the original meaning did not change.
Sometimes, specific words were slightly modified in the target language (e.g., "bush" instead of "hedge") to ensure that all participants understood the instructions well. 
Based on these adaptations, the TANGO--CC could be applied in 17 communities and 13 different languages [@bohn2024universal]. In the following, we describe how researchers can use and customize the TANGO--CC in more detail.

## Features of the TANGO--CC

@@

The task consists of three different trial types: training 1, training 2, and test trials (see Figure \@ref(fig:fig1)).
In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
The balloon falls down to the ground. The eyes of the agent follow the movement of the balloon in a way that the balloon center and the pupil center always align.
Depending on the trial type, participants have different visual access to the balloon's position.
In training 1, participants see the full trajectory of the balloon and directly have to click the balloon itself.
In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
The first trial of each type contains an audio description of the presented events (see Supplements).
Notably, the instructions explicitly state that the agent is looking at the balloon.

@@

The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
For the balloon positions, the entire width of the screen (1920 in "SVG units") is divided into ten bins.
Exact coordinates (value between 0 for the far left and 1920 for the far right) within each bin are then randomly generated.
The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
If the total number of trials is not divisible by the number of unique elements, some elements (*i.e.,* some agents, balloon colors, bins) are randomly repeated to make up for the remainder.

@@

When researchers visit the TANGO--CC's website 
(<https://ccp-odc.eva.mpg.de/tango-cc/>), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1). 
To add a new language, researchers have two options: 
(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds > custom) and select "Custom" in the language drop-down menu.
For detailed instructions, see the TANGO--CC's manual (<https://ccp-odc.eva.mpg.de/tango-cc/manual.html>). 
(2) For adding a new language in the online version of the task, researchers can contact the first author of this paper. Please note that this option requires new audio recordings by the interested researchers, which will then be openly available for all users of the task.
All written instructions in the task are solely for the research assistant to help them guide participants through the task; these instructions are solely available in English. 
The task can either be started with the default settings or further customized by adapting the number of trials, agents, and background scenes.
The default settings use the version applied in @bohn2024universal based on the selected language (see Supplements).

@@

The source code of the task is openly available on GitHub (<https://github.com/ccp-eva/tango-cc>). 
By directly editing the `HTML` and `JavaScript` code, researchers can further modify the task as needed.

We created a public OSF page (https://doi.org/10.17605/OSF.IO/P2EGU) on which we plan to collect data sets that used the TANGO-CC.
Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.

@@

apa_table(
  lang,
  caption = "Current language options available for the audio instructions in the TANGO--CC", 
  note = "In cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers. For example, the English instructions are available in five different versions. * Please note that audio instructions are available in Shona but no data of this version is included in the present data set."
)
```

(ref:figlab2) **Screenshot of the customizable components of the TANGO--CC.** Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.

@@

The task was implemented in `JavaScript`, `HTML`, and `CSS` and is presented as a web app.
It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (though please note that configurations of browsers and JavaScript may change in the future).
Participant's responses can be recorded on a touchscreen or with a mouse or trackpad.
The online version of the task can be used for unsupervised data collection (for example, using online platforms like *Prolific*; see @prein2023tango). The task can be shared easily internationally by providing the URL. 
Importantly, the web app implementation does not require a working WIFI connection: An offline version of the task can be downloaded and quickly set up for devices that support Node.js (<https://nodejs.org/en>).
This is an especially useful feature for researchers working in locations with limited internet access.

The stimuli are embedded as Scalable Vector Graphics (SVG; an image format that stores image elements via mathematical formulas based on points and lines on a grid).
SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant. 
Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of the task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (*i.e.,* in test trials, when they click the hedge).
Furthermore, clicks are only registered after the voice recordings stop playing.
An audio reminder is played again if no click is registered within 5 seconds.

@@

We used the data set from @bohn2024universal for the psychometric evaluation of the TANGO--CC.
The data set contains a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children, aged 2.5 to 11 years.
Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
@bohn2024universal carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions) on a touchscreen device.
Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
For further details on the communities, participant information, and data collection procedures, see the supplements of @bohn2024universal.

@@

(ref:figlab3) **Variability measured by the TANGO--CC.** Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type. Imprecision is defined as the distance between the participant's click and the balloon's center in units of balloon width. For a depiction of each trial's procedure, see Figure \@ref(fig:fig1).

@@

To formally estimate the effect of trial type on performance in the TANGO--CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
All analyses were run in `r R.version$version.string` [@rcoreteam2024language].
GLMMs were fitted with default priors using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
The model included random effects for trial type by community (model notation in `R: imprecision ~ trialtype + (trialtype | community)`), and imprecision was modeled by a `lognormal` distribution.
We inspected the posterior distribution (mean and 95% Credible Interval (CrI)) for the trial type estimates.

@@

[^1]: Please note that the TANGO--CC measures imprecision in gaze following.
Therefore, a negative sign indicates that children showed less imprecision (*i.e.,* were more precise) in the training trials than in the test trials.

@@

(ref:figlab4) **Reliability of the TANGO--CC by community.** Internal consistency estimates by community, following three different approaches. In the odd-even split, the size of points reflects the sample size in each community. In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.

@@

The TANGO--CC measures imprecision in gaze following across individuals, ages, and communities.
Children’s imprecision in gaze following showed highly similar result patterns across communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
Furthermore, the task showed satisfactory to high reliability across all communities.
Therefore, the TANGO--CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.

>>>>

---
title: "Measuring variation in gaze following across communities, ages, and individuals — a showcase of the TANGO-CC"
shorttitle: "measuring gaze following across communities"

@@

    affiliation   : "2,10"

@@

@@

    affiliation   : "14"

@@

affiliation:
  - id            : "1"
    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany"
  - id            : "3"
    institution   : "School of Psychology, University of Auckland, New Zealand"
  - id            : "4"
    institution   : "Université Marien Ngouabi, Republic of the Congo"
  - id            : "5"
    institution   : "Department of Psychology, Stanford University, USA"
  - id            : "6"
    institution   : "School of Psychology, University of Plymouth, UK"
  - id            : "7"
    institution   : "Department of Psychology, Koç University, Türkiye"
  - id            : "8"
    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK"
  - id            : "9"
    institution   : "Department of Psychology and Social Work, University of Namibia, Namibia"
  - id            : "10"
    institution   : "Department of Psychology, Georgia State University, USA"
  - id            : "11"
    institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
  - id            : "12"
    institution   : "Department of Psychology, University of York, UK"
  - id            : "13"
    institution   : "Budongo Conservation Field Station, Uganda"
  - id            : "14"
    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
  - id            : "+"
    institution   : "joint last author"

abstract: | 
            Cross-cultural studies are crucial for investigating the cultural variability and universality of cognitive developmental processes. However, cross-cultural assessment tools in cognition across languages and communities are limited. This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO-CC). The task was developed and psychometrically assessed in one cultural setting and, with input of local collaborators, adapted for cross-cultural data collection. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community. The TANGO-CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities. Within-community variation outweighed between-community variation. We provide an open-source website for researchers to customize and use the task (https://ccp-odc.eva.mpg.de/tango-cc). The TANGO-CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.

@@

The approaches that researchers can take to collect cross-cultural data lie on a continuum: the decision for a specific method partly depends on whether researchers aim to increase the *depth* (culture specificity) or *breadth* (standardization across multiple communities) of their work [@amir2020crosscultural].
At one extreme, researchers translate the psychological construct into a separate design or task for each community (termed "assembly"; @he2012bias, @waschl2022crosscultural).
While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible to study a multitude of communities as it becomes too demanding and time-consuming.
Furthermore, the results are limited to each community and absolute task scores might not be comparable across communities.
A study following this approach is @wefers2023universality who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions. 
While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, @wefers2023universality reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (i.e., emphasis on body stimulation) parenting styles. 
By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.

At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed "adoption" and "adaptation", respectively; @he2012bias, @waschl2022crosscultural).
This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; @gagarina2012main), which assesses narrative abilities in mono- and multilingual children. 
Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust, and suitable for cross-linguistic comparisons [@gagarina2012main], and new and revised language versions are continuously added to the MAIN database [@gagarina2020new].

The present paper aims to describe the development and psychometric properties of a social cognition task that can be adapted to diverse communities.
On the continuum described above, our task lies more toward standardized approaches but allows for some customization of the stimuli to each local community.
The task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
Gaze following develops early in infancy [@delbianco2019developmental; @tang2024slow] and contributes to social learning, communication, and collaboration [@shepherd2010following; @tomasello2007reliance; @bohn2018common; @hernik2019infant].
Identifying the attentional focus of a conversational partner facilitates language development [@brooks2015connecting; @carpenter1998social; @mundy2007individual], as children might use gaze to identify the referent of a new word [@brooks2005development].

One of the main open questions is the impact of social-environmental and cultural factors on gaze following [@astor2022gaze], but studies on variation in gaze following across communities are rare. 
Recently, @brooks2020enhanced found that Deaf infants show increased gaze following compared to hearing infants, underlining the importance of visual-communicative signals for Deaf children. 
@callaghan2011early investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38), and India (n = 65). 
In their setup, an agent looked at a toy behind (experimental condition) or a sticker in front of (control condition) a barrier, and children's crawling toward the barrier to follow the agent's gaze was assessed.
While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier than in front of it.
@hernik2019infant studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
Even though face-to-face interactions are less common in parent-child interactions in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
@astor2022maternal analyzed the effects of maternal postpartum depression on gaze following in 9-month-olds from Bhutan and Sweden. While infants showed similar gaze following rates in both countries, maternal postpartum depression was associated with reduced gaze following only in the Swedish sample. 
Beyond gaze following, some studies conducted in the Global South have investigated opportunities for mutual eye gaze and factors influencing joint attention [see @akhtar2008privileging]. 
For example, Kaluli infants in Papua New Guinea are often carried facing away from their mothers so infants and caregivers share mutual gaze less frequently [@ochs1984language]. @childers2007jointa studied Ngas-speaking infants in Nigeria and found no effect of the caregivers’ carrying style (usually on the back) on children’s joint attention tendencies.

While these studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and – more importantly – does not allow for studying individual-differences. 
A more comprehensive cross-cultural study on gaze following was recently conducted by @bohn2024universal. The researchers tested the universality of gaze following by studying 17 different communities on five continents and found evidence for a similar processing mechanism across communities.

The task presented in this manuscript was developed for the study by @bohn2024universal and is based on a previously established gaze-following task called 'TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by @prein2024tango.
The TANGO measures how precisely participants locate an agent's attentional focus.
It reliably measured individual differences in a German child sample and an English-speaking remote adult sample [@prein2024tango].
However, we cannot claim the task's generalizability and reliability based on a mono-cultural sample. 
This paper showcases the TANGO-CC (TANGO - Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities [@bohn2024universal].
We describe the task's development and provide a tutorial for the open-source website (<https://ccp-odc.eva.mpg.de/tango-cc/>).

@@

The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity [@prein2024tango].
During this process, the cross-cultural adaptation of the task was prepared by a team of cross-cultural psychologists and cognitive scientists. 
In this paper, we assess the TANGO-CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from @bohn2024universal.
In the following, we describe the different steps in detail.

The TANGO-CC is a screen-based, interactive picture book with cartoon-like line drawings (see Figure \@ref(fig:fig1)). Previous gaze studies have successfully implemented tasks with (schematic) line drawings for both children and adults [e.g., @anderson1997preschoolers; @doherty2009rapid; @doherty1999new; @kingstone2000reflexive; @lee1998children].
The TANGO-CC measures the imprecision with which participants locate a balloon by following an agent’s gaze. 
Participants click or touch the location on the screen where they believe the balloon to be.
Precision is measured as the distance between the participant’s click on the screen and the balloon’s real position.

During the task development, we decided to implement the task's main functionality independently of the task's appearance. 
We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures. 
As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged (i.e., no coordination values for animation are hard-coded into the task's source code). 
After having programmed this "backbone" functionality of the task (i.e., animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, agent faces).

This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid [@prein2024tango].
While children became more precise in locating the agent's attentional focus with age, individuals differed across all age groups and showed no floor- or ceiling effects.
In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
In a computational cognitive model, @prein2024variation described gaze following as a form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
These connections to related constructs indicate the task's convergent validity in the German child sample.

To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with input from local researchers and research assistants. 
The stimulus pool was adjusted and expanded until the researchers and research assistants from each target community judged the selected stimuli to be representative of the local population and typical accommodation (see Figure \@ref(fig:fig2)).
Audio instructions were translated from English or German into the corresponding local language(s).
By back-translating these instructions, we ensured the original meaning did not change.
Sometimes, specific words were slightly modified in the target language (e.g., "bush" instead of "hedge") to ensure that all participants understood the instructions well. 
Based on these adaptations, the TANGO-CC could be applied in 17 communities and 13 different languages [@bohn2024universal]. In the following, we describe how researchers can use and customize the TANGO-CC in more detail.

## Features of the TANGO-CC

@@

The task consists of three different trial types: training 1, training 2, and test trials (see Figure \@ref(fig:fig1)).
In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
The balloon falls down to the ground. The eyes of the agent follow the movement of the balloon in a way that the balloon center and the pupil center always align.
Depending on the trial type, participants' visual access to the balloon's position varies.
This experimental design builds on existing gaze following paradigms that have used barriers or obstacles [e.g., @butler2000infant; @dunphy-lelii2004infants; @franco2001toddlers; @moll200412].
In training 1, participants see the full trajectory of the balloon and directly have to click the balloon itself.
In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.

The first trial of each type contains an audio description of the presented events (see Supplements).
Notably, the instructions explicitly state that the agent is looking at the balloon.
This ensures all participants understand the purpose of the task, and minimizes learning effects (increasing comparability between earlier and later trials; avoiding that participants notice the gaze cue only after e.g. half of the trials). 
The TANGO-CC measures *how precisely* participants use the gaze cue, rather than *if* they notice it in the first place.

@@

The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
For the balloon positions, the entire width of the screen (1920 in "SVG units") is divided into ten bins.
Exact coordinates (value between 0 for the far left and 1920 for the far right) within each bin are then randomly generated.
The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
If the total number of trials is not divisible by the number of unique elements, some elements (i.e., some agents, balloon colors, bins) are randomly repeated to make up for the remainder.

@@

When researchers visit the TANGO-CC's website 
(<https://ccp-odc.eva.mpg.de/tango-cc/>), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1). 
To add a new language, researchers have two options: 
(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds > custom) and select "Custom" in the language drop-down menu.
For detailed instructions, see the TANGO-CC's manual (<https://ccp-odc.eva.mpg.de/tango-cc/manual.html>). 
(2) For adding a new language in the online version of the task, researchers can contact the first author of this paper. Please note that this option requires new audio recordings by the interested researchers, which will then be openly available for all users of the task.
All written instructions in the task are solely for the research assistant to help them guide participants through the task; these instructions are solely available in English. 
The task can either be started with the default settings or further customized by adapting the number of trials, agents, and background scenes.
The default settings use the version applied in @bohn2024universal based on the selected language (see Supplements).

@@

The source code of the task is openly available on GitHub (<https://github.com/ccp-eva/tango-cc>). 
By directly editing the `HTML` and `JavaScript` code, researchers can further modify the task as needed. 
To ensure the accessibility of the TANGO–CC long-term, we have additionally stored the source code on Zenodo (https://zenodo.org/doi/10.5281/zenodo.13643836).

We created a public OSF page (https://doi.org/10.17605/OSF.IO/P2EGU) on which we plan to collect data sets that used the TANGO-CC.
Researchers who have collected data using the TANGO-CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.

@@

apa_table(
  lang,
  caption = "Current language options available for the audio instructions in the TANGO-CC", 
  note = "In cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers. For example, the English instructions are available in five different versions. * Please note that audio instructions are available in Shona but no data of this version is included in the present data set."
)
```

(ref:figlab2) **Screenshot of the customizable components of the TANGO-CC.** Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.

@@

The task was implemented in `JavaScript`, `HTML`, and `CSS` and is presented as a web app.
It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (though please note that configurations of browsers and JavaScript may change in the future).
Participant's responses can be recorded on a touchscreen or with a mouse or trackpad.
The online version of the task can be used for unsupervised data collection (for example, using online platforms like *Prolific*; see @prein2024tango). The task can be shared easily internationally by providing the URL. 
Importantly, the web app implementation does not require a working WIFI connection: An offline version of the task can be downloaded and quickly set up for devices that support Node.js (<https://nodejs.org/en>).
This is an especially useful feature for researchers working in locations with limited internet access.

The stimuli are embedded as Scalable Vector Graphics (SVG; an XML format that describes elements in mathematical formulas based on points and lines on a grid).
SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant. 
Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of the task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
Furthermore, clicks are only registered after the voice recordings stop playing.
An audio reminder is played again if no click is registered within 5 seconds.

@@

We used the data set from @bohn2024universal for the psychometric evaluation of the TANGO-CC.
The data set contains a sample of *N* = `r sample_table[sample_table$Community == "Total",]$Total` children, aged 2.5 to 11 years (see supplements).
Participants came from 17 communities on five continents, in rural and urban settings, with varying degrees of market integration and technology exposure.
@bohn2024universal carried out 19 trials (1 training 1, 2 training 2, and 16 test trials, of which the first of each type had audio instructions) on a touchscreen device.
Faces, backgrounds, and languages were chosen by researchers and assistants with experience in the specific community.
For further details on the communities, participant information, and data collection procedures, see the supplements of @bohn2024universal.

@@

(ref:figlab3) **Variability measured by the TANGO-CC.** Mean imprecision in locating the agent's attentional focus by community (alphabetically) and trial type. Imprecision is defined as the distance between the participant's click and the balloon's center in units of balloon width. For a depiction of each trial's procedure, see Figure \@ref(fig:fig1).

@@

To formally estimate the effect of trial type on performance in the TANGO-CC, we fitted a generalized linear mixed model (GLMM) predicting the task performance by trial type (reference category: test trials).
All analyses were run in `r R.version$version.string` [@rcoreteam2024language].
GLMMs were fitted with default priors using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
The model included random effects for trial type by community (model notation in `R: imprecision ~ trialtype + (trialtype | community)`), and imprecision was modeled by a `lognormal` distribution.
We inspected the posterior distribution (mean and 95% Credible Interval (CrI)) for the trial type estimates.

@@

[^1]: Please note that the TANGO-CC measures imprecision in gaze following.
Therefore, a negative sign indicates that children showed less imprecision (i.e., were more precise) in the training trials than in the test trials.

@@

(ref:figlab4) **Reliability of the TANGO-CC by community.** Internal consistency estimates by community, following three different approaches. In the odd-even split, the size of points reflects the sample size in each community. In the stratified approach with and without age correction, density curves show the posterior distributions of the GLMM.

@@

The TANGO-CC measures imprecision in gaze following across individuals, ages, and communities.
Children’s imprecision in gaze following showed highly similar result patterns across communities: children performed better in the training than the test trials, and within-community variation greatly exceeded between-community variation.
Furthermore, the task showed satisfactory to high reliability across all communities.
Therefore, the TANGO-CC is a suitable task to capture individual differences in social-cognitive development in diverse communities.
